---
title: "Schedule"
bibliography: lectures/data_politics_2024.bib
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(flextable)
library(ftExtra)
gdtools::register_gfont(family = "Roboto")
set_flextable_defaults(font.family = "Roboto")
```

Below are the Topics, Readings, and Assignment schedules for the course. Materials for each week will be posted on the course website, with links appearing in the Readings schedule below. In a few cases, PDFs will be uploaded to the course Canvas site.

Readings, lecture slides, and related materials will be posted on each week's page, which can be reached either by clicking on the week in the Topics schedule below or by clicking on the week on the [Materials](materials.qmd) page.

## Topics Overview

```{r}
#| label: schedule_data
#| include: false

schedule_data <- tribble(
        ~Week, ~Date, ~methods, ~applied, ~comp,
        "1", "2/6", "Introduction", "", "Introduction to `R`",
        "1", "2/8", "Logic of Experiments", "", "`R` Basics",
        #      "2", "2/13", "Data Visualization", "Intergroup Prejudice", "`ggplot2` Basics",
        #      "2", "2/15", "Estimation", "Intergroup Prejudice", "Data Wrangling with `dplyr`",
        "3", "2/22", "Data Visualization", "Intergroup Prejudice", "`ggplot2` Basics",
        #      "3", "2/22", "Sampling Distributions", "Political Participation", "Base R",
        "4", "2/27", "Estimation & Sampling Distributions", "Partisanship vs Ideology", "Data Wrangling with `dplyr`",
        # "4", "2/27", "Sampling Distributions", "Partisanship vs Ideology", "Data Wrangling with `dplyr`",
        "4", "2/29", "Inference", "Partisanship vs Ideology", "Functions & Iteration",
        "5", "3/5", "Measurement: Asking Questions", "Changing Political Beliefs", "Data Types and Recoding Data",
        "5", "3/7", "Measurement: Measurement Error", "Changing Political Beliefs", "Data Types and Recoding Data",
        "6", "3/12", "Experimental Design: Stratification", "Combatting Electoral Fraud", "`randomizr` package",
        "6", "3/14", "Experimental Design: Clustering", "Combatting Electoral Fraud", "`randomizr` package",
        "7", "3/19", "Statistical Power", "Authoritarian Censorship", "Simulations",
        "7", "3/21", "Choosing Experimental Designs", "Authoritarian Censorship", "Simulations",
        "8", "4/2", "Linear Models and Experiments", "Misinformation", "Linear Modeling with `lm`",
        "8", "4/4", "Covariate Adjustment", "Misinformation", "`estimatr` package",
        "9", "4/9", "Public Opinion Surveys", "Affective Polarization", "`survyr` package",
        "9", "4/11", "Survey Methodology", "Affective Polarization", "`survyr` package",
        "10", "4/16", "Survey Non-Response", "Non-Response Bias in Recent Elections", " ",
        "10", "4/18", "Addressing Non-Response", "Non-Response Bias in Recent Elections", " ",
        "11", "4/23", "Predictive Modeling", "Predicting Electoral Outcomes", "",
        "11", "4/25", "Modeling and Surveys", "Predicting Electoral Outcomes", "",
        "12", "4/30", "Final Project", " ", " ",
        "12", "5/2", "Final Project", " ", " ",
        "13", "5/7", "Final Project", "", "",
        "13", "5/9", "Final Project", "", "",
        "14", "5/14", "Final Project", " ", " ",
)

```

```{r}
#| label: schedule
#| tbl-cap: Topics Schedule
#| echo: false

flextable(schedule_data) |>
        set_header_labels(
                methods = "Methods Topic",
                applied = "Applied Topic",
                comp = "Computing Topic"
        ) |>
        bold(part = "header") |>
        merge_v(j = ~ Week + applied + applied + comp) |>
        valign(j = ~Week, valign = "center") |>
        align(j = ~Week, align = "center") |>
        hline(i = c(2, 3, 5, 7, 9, 11, 13, 15, 17, 19, 21, 23)) |>
        colformat_md() |>
        fix_border_issues() |>
        autofit()
```

## Readings Schedule

| **Week 1** | **Methods**                           | **Applied**                                       | **Computation**                                                                                                                            |
|------------|---------------------------------------|---------------------------------------------------|--------------------------------------------------------------------------------------------------------------------------------------------|
| 1          | GG pgs 1-30                           |                                                   | RDS [2](https://r4ds.hadley.nz/workflow-basics)                                                                                            |
| 3          | GG pgs 30-45                          | @mousaBuildingSocialCohesion2020                  | RDS [1](https://r4ds.hadley.nz/data-visualize), [3](https://r4ds.hadley.nz/data-transform)                                                 |
| 4          | GG pgs 51-71                          | @barberDoesPartyTrump2019                         | RDS [25.1-25.2](https://r4ds.hadley.nz/functions), [26](https://r4ds.hadley.nz/iteration), [27.5](https://r4ds.hadley.nz/base-r#for-loops) |
| 5          | @stantchevaHowRunSurveys2023          | @broockmanDurablyReducingTransphobia2016          | RDS [12](https://r4ds.hadley.nz/logicals), [13](https://r4ds.hadley.nz/numbers), [14](14)                                                  |
| 6          | GG pgs. 71-80                         | @garbiras-diazAllEyesThem2022                     | `randomizr` [vignette](https://declaredesign.org/r/randomizr/articles/randomizr_vignette.html)                                             |
| 7          | GG pgs 80-85                          | @kingReverseengineeringCensorshipChina2014        |                                                                                                                                            |
| 8          | GG pgs. 95-105                        | @arecharUnderstandingCombattingMisinformation2023 |                                                                                                                                            |
| 9          | Ch. 4 in @grovesSurveyMethodology2009 | @ahlerPartiesOurHeads2018                         | `srvyr` [vignette](http://gdfe.co/srvyr/articles/srvyr-vs-survey.html)                                                                     |
| 10         | Ch. 6 in @grovesSurveyMethodology2009 | @cohnnate2023CitrinAward2023                      |                                                                                                                                            |
| 11         |                                       | @jenningsElectionPollingErrors2018                |                                                                                                                                            |

## Assignments Schedule

```{r}
#| label: assignments_data
#| include: false

assignments_data <- tribble(
        ~Week, ~due_date, ~Assignment,
        "2", "2/12", "Reading Quiz",
        "2", "2/14", "Tutorial",
        # "3", "2/21", "Reading Quiz",
        # "3", "2/21", "Tutorial",

        "4", "2/26", "Reading Quiz",
        "4", "2/28", "Tutorial",
        "4", "2/29", "*Problem Set 1*",
        "5", "3/4", "Reading Quiz",
        "5", "3/8", "*Problem Set 2*",
        "7", "3/18", "Reading Quiz",
        "7", "3/21", "Tutorial",
        "7", "3/22", "*Problem Set 3*",
        "8", "4/2", "Reading Quiz",
        "8", "4/3", "Tutorial",
        "9", "4/9", "Reading Quiz",
        "9", "4/10", "Tutorial",
        "9", "4/11", "*Problem Set 4*",
        "10", "4/16", "Reading Quiz",
        "11", "4/25", "*Problem Set 5*",
        "13", "5/9", "*Problem Set 6*",
        "14", "5/14", "*Class Project Writeup*"
)

## function to find index of row of last row of each week
find_last_row <- function(x) {
        x |>
                mutate(row_num = 1:nrow(x)) |>
                group_by(Week) |>
                summarise(last_row = max(row_num)) |>
                pull(last_row)
}


```

```{r}
#| label: assignments
#| tbl-cap: Assignments Schedule
#| echo: false

flextable(assignments_data) |>
        set_header_labels(
                due_date = "Due Date",
                Assignment = "Assignment"
        ) |>
        bold(part = "header") |>
        merge_v(j = ~ Week + due_date + Assignment) |>
        valign(j = ~Week, valign = "center") |>
        align(j = ~Week, align = "center") |>
        hline(i = find_last_row(assignments_data)) |>
        colformat_md() |>
        fix_border_issues() |>
        autofit()
```
